Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2022-12-05 paper/manuscript.Rmd
change the order of dependent variables / update intro
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Effective teaching involves experts and novices dynamically interacting with each other [@byrne_2011]. Typically, information flows between experts and novices is mostly not unidirectional (i.e., from experts to novices) but rather bidirectional and interactive [@charbonneau_2022]. Experts adapt their behaviour to novices and scaffold the acquisition process of complex skills, and novices are actively participating in the learning process [@okazaki_2019; @flynn_2022].

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions [@pezzulo_2019], including teaching contexts. When caregivers were teaching how to use a novel toy to their infants, they tended to exaggerate the movement paths [@brand_2002]. Such exaggeration was observed not only towards infant learners but also when adults were interacting with adult learners [@mcellin_2017; @uther_2007]. For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own [@mcellin_2017].

Recent evidence from parent-infant interactions suggests that such pedagogical action modulations are sensitive to the skill levels of learners. @fukuyama_2015 found that mothers who were demonstrating how to use nesting cups to their infants dynamically modulated their demonstration according to the infants' object manipulation skills. For example, the mothers exaggerated their movements when their infants failed to produce expected actions whereas the mothers did not produce such exaggeration when their infants did not have the motor skills needed to produce the required actions. To the best of our knowledge, it is unknown whether people teaching skills to adult learners also adjust their demonstrations as a function of the learners' demonstrated skills.

To address this question, in the current study we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on the skill level of the novice learners. In our previous research (Tominaga et al., under review), we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To have experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists The recordings were made based on the performance data from our previous study (Tominaga et al., under review). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (*Fig \ref{fig:stim}*). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

We hypothesised that expert pianists would exaggerate their performance only when specific techniques (i.e., either articulation or dynamics, or both) were missing in the recordings. More precisely, expert pianists would exaggerate articulation (i.e., producing longer legato and shorter staccato) when articulation was not implemented in the recordings whereas expert pianists would exaggerate dynamics (i.e., producing  louder forte and softer piano, and larger contrast between forte and piano) when dynamics was not implemented in the recordings. If both articulation and dynamics were missing, we predicted that expert pianists would exaggerate both aspects.

@@

The dependent variables were computed from MIDI data for data analysis. Interonset intervals (IOIs) are the intervals between onsets of adjacent notes and provide a measure of tempo. Key-overlap time (KOT) is the difference between the offset time (i.e., key release time) of the current tone and the onset time of the ensuing tone and is a measure for the smoothness of musical sequences. A positive value indicates smooth legato style due to overlap between the current and ensuing tone whereas a negative value indicates sharp staccato style due to separation between the current and ensuing note. Tone intensity is assessed  by key velocity (KV) and measures the loudness of a musical note. A higher value indicates forte style whereas a lower value indicates piano style. The value of KV in MIDI varies between 0 (minimum) and 127 (maximum). Also, KV difference was calculated by subtracting the KV value of the current note from that of the following note. We particularly focused on specific points where each subcomponent changed from one to the other (i.e., forte to piano or piano to forte) to measure dynamics contrast between forte and piano.

Data processing and statistical analysis were performed in R version 4.0.5. For statistical analysis, we included 8th notes with expressive notations only. Pitch errors were identified by comparing the sequence of  musical notes produced by a participant with the sequence of musical notes according to the sheet music. Pitch errors included extra, missing or substituted tones and were manually removed by using the *editData* R package. For note onsets,  `r round(nrow(dt_error_onset)/(20*16)*100, 2)` % of the trials contained at least one pitch error (extra notes: `r round(nrow(error_extra_onset)/(20*16)*100, 2)` %, missing notes: `r round(nrow(error_missing_onset)/(20*16)*100, 2)` %, substituted notes: `r round(nrow(error_sub_onset)/(20*16)*100, 2)` %). For note offsets,  `r round(nrow(dt_error_offset)/(20*16)*100, 2)` % of the trials contained at least one pitch error (extra notes: `r round(nrow(error_extra_offset)/(20*16)*100, 2)` %, missing notes: `r round(nrow(error_missing_offset)/(20*16)*100, 2)` %, substituted notes: `r round(nrow(error_sub_offset)/(20*16)*100, 2)` %). We found that some participants did not precisely follow the sheet music (e.g., they held some notes longer than notated), therefore the order of offsets did not correspond to that of onsets. We considered these as errors and removed the erroneous notes even if the order of onsets was correct. As a result, less than 1 % of total responses were removed. After removing pitch errors, we removed outliers for IOIs, KOT, KV and KV Difference, defined as values more than 3 standard deviations from the mean of each dependent variable. For each dependent variable, this resulted in less than 2 % of overall responses being removed as outliers.

First, we performed a 2 x 2 repeated-measures analysis of variance (ANOVA) with the factors Articulation (present vs. absent) and Dynamics (present vs absent) for each dependent variable (i.e.., IOIs, KOT, KV, KV Difference). The *aov_ez* function in the *afex* R package was used for a repeated-measures ANOVA. For post-hoc comparisons on the estimated marginal means, we used the  *emmeans* R package.

@@

# save plots
ggsave(here("paper/image", "ioi_ca_plot.png"), plot = ioi_ca_plot, dpi = 300, height = 5)
img_ioi_ca_plot <- image_read(here("paper/image", "ioi_ca_plot.png"), density = 300)
```

@@

```{r vel-diff-bl-plot, include = FALSE}
ftop_ca_plot <- ggplot(vel_diff[Subcomponent2 == "FtoP" & Category == "baseline" | Subcomponent2 == "FtoP" & Category == "both" | Subcomponent2 == "FtoP" & Category == "art_only"], aes(x = factor(Category, level = c("baseline", "art_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KV Difference (-127-127)", title = "KV Difference - FtoP") + scale_y_continuous(breaks = seq(-40, 10, 10), limits = c(-40, 10)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

>>>>

Effective teaching involves experts and novices dynamically interacting with each other [@byrne_2011]. During a skill acquisition process, experts regularly monitor novices' actions and intervene by adapting their behaviour to novices' observed abilities until novices can perform the actions independently without the help of experts [@mermelshtine_2017]. Particularly, it is important for experts to find what novices have a problem from their failed attempt and to modify their behaviour [@ugur_2015; @zukow-goldring_2007].

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions [@pezzulo_2019], including teaching contexts. When mothers were teaching how to use a novel toy to their infants, they tended to demonstrate slowly and produce wide and expansive movements compared with when they were demonstrating to adults [@brand_2002]. Such exaggeration was observed not only towards infant learners but also when knowledgeable adults were interacting with adult learners [@mcellin_2017]. For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own.

Recent evidence from parent-infant interactions suggests that such pedagogical action modulations are sensitive to the skill level of learners [@fukuyama_2015] In this study, mothers were asked to demonstrate demonstrate a cup-nesting task to their infants. There were four cups with different colour and size. The mothers showed how to stack and fit the nesting cups so that infants could reproduce the actions by themselves. The findings showed that the mothers dynamically modulated their demonstration according to the infants' object manipulation skills. For example, the mothers exaggerated their movements when their infants failed to produce expected actions whereas the mothers did not produce such exaggeration when their infants did not have the motor skills needed to produce the required actions. To the best of our knowledge, it is unknown whether people teaching skills to adult learners also adjust their demonstrations as a function of the learners' demonstrated skills.

To address this question, in the current study we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on the skill level of the novice learners. In our previous research (Tominaga et al., accepted), we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To have experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists The recordings were made based on the performance data from our previous study (Tominaga et al., accepted). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (*Fig \ref{fig:stim}*). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

Evidence from parental scaffolding research suggests that caregivers scaffold infants' learning when the infants failed to produce an expected action [@wood_1975; @zukow-goldring_2007]. Therefore, we hypothesised that expert pianists would exaggerate their performance only when specific techniques (i.e., either articulation or dynamics, or both) were missing in the recordings. More precisely, expert pianists would exaggerate articulation (i.e., producing longer legato and shorter staccato) when articulation was not implemented in the recordings whereas expert pianists would exaggerate dynamics (i.e., producing  louder forte and softer piano, and larger contrast between forte and piano) when dynamics was not implemented in the recordings. If both articulation and dynamics were missing, we predicted that expert pianists would exaggerate both aspects.

@@

The dependent variables were computed from MIDI data for data analysis. Key-overlap time (KOT) is the difference between the offset time (i.e., key release time) of the current tone and the onset time of the ensuing tone and is a measure for the smoothness of musical sequences. A positive value indicates smooth legato style due to overlap between the current and ensuing tone whereas a negative value indicates sharp staccato style due to separation between the current and ensuing note. Tone intensity is assessed  by key velocity (KV) and measures the loudness of a musical note. A higher value indicates forte style whereas a lower value indicates piano style. The value of KV in MIDI varies between 0 (minimum) and 127 (maximum). Also, KV difference was calculated by subtracting the KV value of the current note from that of the following note. We particularly focused on specific points where each subcomponent changed from one to the other (i.e., forte to piano or piano to forte) to measure dynamics contrast between forte and piano. Interonset intervals (IOIs) are the intervals between onsets of adjacent notes and provide a measure of tempo.

Data processing and statistical analysis were performed in R version 4.0.5. For statistical analysis, we included 8th notes with expressive notations only. Pitch errors were identified by comparing the sequence of  musical notes produced by a participant with the sequence of musical notes according to the sheet music. Pitch errors included extra, missing or substituted tones and were manually removed by using the *editData* R package. For note onsets,  `r round(nrow(dt_error_onset)/(20*16)*100, 2)` % of the trials contained at least one pitch error (extra notes: `r round(nrow(error_extra_onset)/(20*16)*100, 2)` %, missing notes: `r round(nrow(error_missing_onset)/(20*16)*100, 2)` %, substituted notes: `r round(nrow(error_sub_onset)/(20*16)*100, 2)` %). For note offsets,  `r round(nrow(dt_error_offset)/(20*16)*100, 2)` % of the trials contained at least one pitch error (extra notes: `r round(nrow(error_extra_offset)/(20*16)*100, 2)` %, missing notes: `r round(nrow(error_missing_offset)/(20*16)*100, 2)` %, substituted notes: `r round(nrow(error_sub_offset)/(20*16)*100, 2)` %). We found that some participants did not precisely follow the sheet music (e.g., they held some notes longer than notated), therefore the order of offsets did not correspond to that of onsets. We considered these as errors and removed the erroneous notes even if the order of onsets was correct. As a result, less than 1 % of total responses were removed. After removing pitch errors, we removed outliers for KOT, KV, KV Difference and IOIs, defined as values more than 3 standard deviations from the mean of each dependent variable. For each dependent variable, this resulted in less than 2 % of overall responses being removed as outliers.

First, we performed a 2 x 2 repeated-measures analysis of variance (ANOVA) with the factors Articulation (present vs. absent) and Dynamics (present vs absent) for each dependent variable (i.e.., KOT, KV, KV Difference, IOIs). The *aov_ez* function in the *afex* R package was used for a repeated-measures ANOVA. For post-hoc comparisons on the estimated marginal means, we used the  *emmeans* R package.

@@

@@

# save plots
ggsave(here("paper/image", "ioi_ca_plot.png"), plot = ioi_ca_plot, dpi = 300, height = 5)
img_ioi_ca_plot <- image_read(here("paper/image", "ioi_ca_plot.png"), density = 300)
```
```{r vel-diff-bl-plot, include = FALSE}
ftop_ca_plot <- ggplot(vel_diff[Subcomponent2 == "FtoP" & Category == "baseline" | Subcomponent2 == "FtoP" & Category == "both" | Subcomponent2 == "FtoP" & Category == "art_only"], aes(x = factor(Category, level = c("baseline", "art_only", "both")), y = Mean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.15, alpha = 0.5) +
  labs(x = "Category", y = "KV Difference (-127-127)", title = "KV Difference - FtoP") + scale_y_continuous(breaks = seq(-40, 10, 10), limits = c(-40, 10)) +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica")

### 2022-12-05 paper/manuscript.tex
change the order of dependent variables / update intro
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Effective teaching involves experts and novices dynamically interacting with each other (Byrne \& Rapaport, 2011). Typically, information flows between experts and novices is mostly not unidirectional (i.e., from experts to novices) but rather bidirectional and interactive (Charbonneau \& Strachan, 2022). Experts adapt their behaviour to novices and scaffold the acquisition process of complex skills, and novices are actively participating in the learning process (Flynn, 2022; Okazaki, Muraoka, \& Osu, 2019).

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions (Pezzulo et al., 2019), including teaching contexts. When caregivers were teaching how to use a novel toy to their infants, they tended to exaggerate the movement paths (Brand, Baldwin, \& Ashburn, 2002). Such exaggeration was observed not only towards infant learners but also when adults were interacting with adult learners (McEllin, Knoblich, \& Sebanz, 2017; Uther, Knoll, \& Burnham, 2007). For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own (McEllin et al., 2017).

Recent evidence from parent-infant interactions suggests that such pedagogical action modulations are sensitive to the skill levels of learners. Fukuyama et al. (2015) found that mothers who were demonstrating how to use nesting cups to their infants dynamically modulated their demonstration according to the infants' object manipulation skills. For example, the mothers exaggerated their movements when their infants failed to produce expected actions whereas the mothers did not produce such exaggeration when their infants did not have the motor skills needed to produce the required actions. To the best of our knowledge, it is unknown whether people teaching skills to adult learners also adjust their demonstrations as a function of the learners' demonstrated skills.

To address this question, in the current study we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on the skill level of the novice learners. In our previous research (Tominaga et al., under review), we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To have experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists The recordings were made based on the performance data from our previous study (Tominaga et al., under review). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (\emph{Fig \ref{fig:stim}}). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

We hypothesised that expert pianists would exaggerate their performance only when specific techniques (i.e., either articulation or dynamics, or both) were missing in the recordings. More precisely, expert pianists would exaggerate articulation (i.e., producing longer legato and shorter staccato) when articulation was not implemented in the recordings whereas expert pianists would exaggerate dynamics (i.e., producing louder forte and softer piano, and larger contrast between forte and piano) when dynamics was not implemented in the recordings. If both articulation and dynamics were missing, we predicted that expert pianists would exaggerate both aspects.

@@

The dependent variables were computed from MIDI data for data analysis. Interonset intervals (IOIs) are the intervals between onsets of adjacent notes and provide a measure of tempo. Key-overlap time (KOT) is the difference between the offset time (i.e., key release time) of the current tone and the onset time of the ensuing tone and is a measure for the smoothness of musical sequences. A positive value indicates smooth legato style due to overlap between the current and ensuing tone whereas a negative value indicates sharp staccato style due to separation between the current and ensuing note. Tone intensity is assessed by key velocity (KV) and measures the loudness of a musical note. A higher value indicates forte style whereas a lower value indicates piano style. The value of KV in MIDI varies between 0 (minimum) and 127 (maximum). Also, KV difference was calculated by subtracting the KV value of the current note from that of the following note. We particularly focused on specific points where each subcomponent changed from one to the other (i.e., forte to piano or piano to forte) to measure dynamics contrast between forte and piano.

Data processing and statistical analysis were performed in R version 4.0.5. For statistical analysis, we included 8th notes with expressive notations only. Pitch errors were identified by comparing the sequence of musical notes produced by a participant with the sequence of musical notes according to the sheet music. Pitch errors included extra, missing or substituted tones and were manually removed by using the \emph{editData} R package. For note onsets, 31.87 \% of the trials contained at least one pitch error (extra notes: 5.94 \%, missing notes: 24.38 \%, substituted notes: 1.56 \%). For note offsets, 35.31 \% of the trials contained at least one pitch error (extra notes: 5.94 \%, missing notes: 24.38 \%, substituted notes: 5 \%). We found that some participants did not precisely follow the sheet music (e.g., they held some notes longer than notated), therefore the order of offsets did not correspond to that of onsets. We considered these as errors and removed the erroneous notes even if the order of onsets was correct. As a result, less than 1 \% of total responses were removed. After removing pitch errors, we removed outliers for IOIs, KOT, KV and KV Difference, defined as values more than 3 standard deviations from the mean of each dependent variable. For each dependent variable, this resulted in less than 2 \% of overall responses being removed as outliers.

First, we performed a 2 x 2 repeated-measures analysis of variance (ANOVA) with the factors Articulation (present vs.~absent) and Dynamics (present vs absent) for each dependent variable (i.e.., IOIs, KOT, KV, KV Difference). The \emph{aov\_ez} function in the \emph{afex} R package was used for a repeated-measures ANOVA. For post-hoc comparisons on the estimated marginal means, we used the \emph{emmeans} R package.

@@

Experiments which investigated dynamic interactions between experts and novices have been done with the physical presence of both an expert and a novice in the same place (Fukuyama et al., 2015; Okazaki et al., 2019). In the current experiment, expert pianists had only access to their imaginary students and needed to perform in the absence of actual students. Future research should investigate how expert pianists and novices dynamically interact in a situation where they can communicate in real-time and examine how the performance of expert pianists and that of novices are related to each other.

@@

\leavevmode\vadjust pre{\hypertarget{ref-charbonneau_2022}{}}%
Charbonneau, M., \& Strachan, J. W. A. (2022). From {Copying} to {Coordination}: {An Alternative Framework} for {Understanding Cultural Learning Mechanisms}. \emph{Journal of Cognition and Culture}, \emph{22}(5), 451--466. \url{https://doi.org/10.1163/15685373-12340145}

\leavevmode\vadjust pre{\hypertarget{ref-flynn_2022}{}}%
Flynn, E. (2022). {``{Imitation Is} the {Sincerest Form} of''} \ldots{} {Cultural Evolution}, or {Is It}? \emph{Journal of Cognition and Culture}, \emph{22}(5), 436--450. \url{https://doi.org/10.1163/15685373-12340144}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-uther_2007}{}}%
Uther, M., Knoll, M. A., \& Burnham, D. (2007). Do you speak {E-NG-L-I-SH}? {A} comparison of foreigner- and infant-directed speech. \emph{Speech Communication}, \emph{49}(1), 2--7. \url{https://doi.org/10.1016/j.specom.2006.10.003}

>>>>

Effective teaching involves experts and novices dynamically interacting with each other (Byrne \& Rapaport, 2011). During a skill acquisition process, experts regularly monitor novices' actions and intervene by adapting their behaviour to novices' observed abilities until novices can perform the actions independently without the help of experts (Mermelshtine, 2017). Particularly, it is important for experts to find what novices have a problem from their failed attempt and to modify their behaviour (Ugur, Nagai, Celikkanat, \& Oztop, 2015; Zukow-Goldring \& Arbib, 2007).

Exaggeration of movement is often used to signal a communicative intent to others during real-time interactions (Pezzulo et al., 2019), including teaching contexts. When mothers were teaching how to use a novel toy to their infants, they tended to demonstrate slowly and produce wide and expansive movements compared with when they were demonstrating to adults (Brand, Baldwin, \& Ashburn, 2002). Such exaggeration was observed not only towards infant learners but also when knowledgeable adults were interacting with adult learners (McEllin, Knoblich, \& Sebanz, 2017). For example, participants demonstrating to a learner how to play a particular melody on a xylophone increased the amplitude of their movements, compared to playing the same melody on their own.

Recent evidence from parent-infant interactions suggests that such pedagogical action modulations are sensitive to the skill level of learners (Fukuyama et al., 2015) In this study, mothers were asked to demonstrate demonstrate a cup-nesting task to their infants. There were four cups with different colour and size. The mothers showed how to stack and fit the nesting cups so that infants could reproduce the actions by themselves. The findings showed that the mothers dynamically modulated their demonstration according to the infants' object manipulation skills. For example, the mothers exaggerated their movements when their infants failed to produce expected actions whereas the mothers did not produce such exaggeration when their infants did not have the motor skills needed to produce the required actions. To the best of our knowledge, it is unknown whether people teaching skills to adult learners also adjust their demonstrations as a function of the learners' demonstrated skills.

To address this question, in the current study we investigated whether and how expert pianists adapt their pedagogical demonstrations for learners depending on the skill level of the novice learners. In our previous research (Tominaga et al., accepted), we demonstrated that expert pianists modulated their performance when they were asked to teach musical expressive techniques such as articulation and dynamics. In particular, expert pianists exaggerated the contrast between different dynamics (i.e., they made a larger contrast between forte and piano) when they had the intention to demonstrate dynamics. When they had the intention to demonstrate articulation, they exaggerated articulation by producing shorter staccato. In that study, teachers were instructed to teach techniques to hypothetical learners and they did not hear novices' particular performances. This leaves open the question whether pianists would make specific adjustments depending on learners' skills in the way mothers have been shown to adapt demonstrations of actions to their infants' skills. If teachers modulate their demonstrations based on learners' skills, their exaggeration of particular aspects should depend on the learners' actual performance with regard to the techniques to be acquired.

To have experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists The recordings were made based on the performance data from our previous study (Tominaga et al., accepted). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (\emph{Fig \ref{fig:stim}}). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

Evidence from parental scaffolding research suggests that caregivers scaffold infants' learning when the infants failed to produce an expected action (Wood \& Middleton, 1975; Zukow-Goldring \& Arbib, 2007). Therefore, we hypothesised that expert pianists would exaggerate their performance only when specific techniques (i.e., either articulation or dynamics, or both) were missing in the recordings. More precisely, expert pianists would exaggerate articulation (i.e., producing longer legato and shorter staccato) when articulation was not implemented in the recordings whereas expert pianists would exaggerate dynamics (i.e., producing louder forte and softer piano, and larger contrast between forte and piano) when dynamics was not implemented in the recordings. If both articulation and dynamics were missing, we predicted that expert pianists would exaggerate both aspects.

@@

The dependent variables were computed from MIDI data for data analysis. Key-overlap time (KOT) is the difference between the offset time (i.e., key release time) of the current tone and the onset time of the ensuing tone and is a measure for the smoothness of musical sequences. A positive value indicates smooth legato style due to overlap between the current and ensuing tone whereas a negative value indicates sharp staccato style due to separation between the current and ensuing note. Tone intensity is assessed by key velocity (KV) and measures the loudness of a musical note. A higher value indicates forte style whereas a lower value indicates piano style. The value of KV in MIDI varies between 0 (minimum) and 127 (maximum). Also, KV difference was calculated by subtracting the KV value of the current note from that of the following note. We particularly focused on specific points where each subcomponent changed from one to the other (i.e., forte to piano or piano to forte) to measure dynamics contrast between forte and piano. Interonset intervals (IOIs) are the intervals between onsets of adjacent notes and provide a measure of tempo.

Data processing and statistical analysis were performed in R version 4.0.5. For statistical analysis, we included 8th notes with expressive notations only. Pitch errors were identified by comparing the sequence of musical notes produced by a participant with the sequence of musical notes according to the sheet music. Pitch errors included extra, missing or substituted tones and were manually removed by using the \emph{editData} R package. For note onsets, 31.87 \% of the trials contained at least one pitch error (extra notes: 5.94 \%, missing notes: 24.38 \%, substituted notes: 1.56 \%). For note offsets, 35.31 \% of the trials contained at least one pitch error (extra notes: 5.94 \%, missing notes: 24.38 \%, substituted notes: 5 \%). We found that some participants did not precisely follow the sheet music (e.g., they held some notes longer than notated), therefore the order of offsets did not correspond to that of onsets. We considered these as errors and removed the erroneous notes even if the order of onsets was correct. As a result, less than 1 \% of total responses were removed. After removing pitch errors, we removed outliers for KOT, KV, KV Difference and IOIs, defined as values more than 3 standard deviations from the mean of each dependent variable. For each dependent variable, this resulted in less than 2 \% of overall responses being removed as outliers.

First, we performed a 2 x 2 repeated-measures analysis of variance (ANOVA) with the factors Articulation (present vs.~absent) and Dynamics (present vs absent) for each dependent variable (i.e.., KOT, KV, KV Difference, IOIs). The \emph{aov\_ez} function in the \emph{afex} R package was used for a repeated-measures ANOVA. For post-hoc comparisons on the estimated marginal means, we used the \emph{emmeans} R package.

@@

Experiments which investigated dynamic interactions between experts and novices have been done with the physical presence of both an expert and a novice in the same place (Fukuyama et al., 2015; Okazaki, Muraoka, \& Osu, 2019). In the current experiment, expert pianists had only access to their imaginary students and needed to perform in the absence of actual students. Future research should investigate how expert pianists and novices dynamically interact in a situation where they can communicate in real-time and examine how the performance of expert pianists and that of novices are related to each other.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-mermelshtine_2017}{}}%
Mermelshtine, R. (2017). Parent\textendash child learning interactions: {A} review of the literature on scaffolding. \emph{British Journal of Educational Psychology}, \emph{87}(2), 241--254. \url{https://doi.org/10.1111/bjep.12147}

@@

\leavevmode\vadjust pre{\hypertarget{ref-ugur_2015}{}}%
Ugur, E., Nagai, Y., Celikkanat, H., \& Oztop, E. (2015). Parental scaffolding as a bootstrapping mechanism for learning grasp affordances and imitation skills. \emph{Robotica}, \emph{33}(5), 1163--1180. \url{https://doi.org/10.1017/S0263574714002148}

\leavevmode\vadjust pre{\hypertarget{ref-wood_1975}{}}%
Wood, D., \& Middleton, D. (1975). A {Study} of {Assisted Problem-Solving}. \emph{British Journal of Psychology}, \emph{66}(2), 181--191. \url{https://doi.org/10.1111/j.2044-8295.1975.tb01454.x}
